Titeln på avhandlingens språk

### 2023-02-02 body/part1/background.tex
comment

There's more to end-to-end latency than merely the question of where the compute backend is placed, however.
The design of any complex application such as \gls{WCA} involves a multitude of decisions with the potential to influence the system responsiveness as experienced by the user.
These decisions include those on the implementation side (compression standards, algorithms, protocols, etc.), as well as on the infrastructure side (physical network layer, traffic prioritization, etc.).
Existing studies of this class of applications have only recently started to delve more deeply upon these issues~\cite{chen2017empirical,wang2019towards,wang2020scaling,ha2014towards,chen2015early,satyanarayanan2009case,chatzopoulos2017hyperion}.
Recently published models for end-to-end latency of edge computing architectures, on the other hand, are quite complex, while not accounting for the specifics of human-in-the-loop applications and in many cases limited to very constrained scenarios and analyses~\cite{al_zubaidy2015performance,schiessl2017finite,moothedath2022energy2,moothedath2022energy1,moothedath2021energy}.
The present thesis aims to contribute to this body of work by presenting and discussing a viable methodology for the design and evaluation of these systems.

>>>>

There's more to end-to-end latency than merely the question of where the compute backend is placed, however.
The design of any complex application such as \gls{WCA} involves a multitude of decisions with the potential to influence the system responsiveness as experienced by the user.
These decisions include those on the implementation side (compression standards, algorithms, protocols, etc.), as well as on the infrastructure side (physical network layer, traffic prioritization, etc.).
Existing studies of this class of applications have only recently started to delve more deeply upon these issues~\cite{chen2017empirical,wang2019towards,wang2020scaling,ha2014towards,chen2015early,satyanarayanan2009case,chatzopoulos2017hyperion}.
Recently published models for end-to-end latency of edge computing architectures, on the other hand, are quite complex, while not accounting for the specifics of human-in-the-loop applications and in many cases limited to very constrained scenarios and analyses~\cite{al_zubaidy2015performance,schiessl2017finite,moothedath2022energy2,moothedath2022energy1,moothedath2021energy}.
\todo[inline]{%
    Maybe also present ``other'' research on WCA here? E.g.\ other research in WCA has focused on... So-and-so have... blah blah.
}
The present thesis aims to contribute to this body of work by presenting and discussing a viable methodology for the design and evaluation of these systems.
